% Created 2015-02-06 Fri 18:50
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{minted}
\author{Derek Harter}
\date{CSci 515 Spring 2014 \textit{<2015-02-06 Fri>}}
\title{Lecture 04 Notes}
\hypersetup{
  pdfkeywords={},
  pdfsubject={Lecture 04 Notes.},
  pdfcreator={Emacs 24.3.1 (Org mode 8.2.4)}}
\begin{document}

\maketitle

\section{First Session (11 - 11:40)}
\label{sec-1}
\subsection{Functional Programming}
\label{sec-1-1}
\begin{itemize}
\item 6.1 To promote software reusability, every function should be
limited to performing a single well define task, and the name of the
function should express the task effectively.
\item 6.2 If you cannot choose a concise name that expresses a function's
task, your function might be attempting to perform too many diverse
tasks.  It's usually best to break such a function into several
smaller functions.
\end{itemize}

Functions serve several purposes from the point of view of the
computer science and the application developer:

\begin{enumerate}
\item Functions encapsulate an algorithm or procedure.
\item Functions can be black boxes that help reduce complexity.  You can
build more complex algorithms on top of simple functions, without
worrying about the details of how the functions you use are
implemented.
\item Functions allow for reuse of code, and help to avoid code repetition.
\end{enumerate}

For example, it can be very complex to write an algorithm to compute
mathematical functions, such as the sin() trigonometric function, on a
digital computer.  However, there are standard libraries of math
functions that you can use that implement the sin() function for you.
When you use a library that someone else has written, you are using
the functions as black boxes.  You know what the function should take
as input, what it does, and what its result should be.  But you do not
need to concern yourself with the messy details of how it achieves its
result.  Likewise, using standard libraries are examples of a type of
reuse.  The functions are written one time by experts, but reused over
and over again in many programs.

As a programmer you can get the same benefits by writing functions
yourself.  You can write a function once, and reuse it in many
locations in your code.  This is an example of a good programming
practice known as Don't Repeat Yourself (the DRY principle).  You
should (almost) never have code repeated in 2 or more places.  Once
you have the urge to repeat a piece of code, you have probably
identified a small procedure or task that should be encapsulated
inside of a function, that can be called when needed.

Likewise user defined functions help manage complexity when writing
complex algorithms.  There is a design strategy known as functional
decomposition.  Basically, when approaching a problem in this manner,
you try and break down the ultimate task into smaller sub-tasks.  If
those sub-tasks are complex, you further break them down into
sub-sub-tasks.  You repeat this decomposition until you have defined
problems that are simple enough to understand and code directly as
small functions.  Then you solve the larger problems by stringing
together and reusing your functions.

It takes skill and practice to learn how best to do such
decomposition, but it is fundamental to learning how to solve real
problems that are often complex and messy.  Functional decomposition
allows you to encapsulate the messiness of the details in black boxes,
as functions, then forget about that messiness to solve larger issues,
on up till you address your ultimate problem.

Being able to break down a problem into good sub-problems, that can be
easily solved individually and then combined into larger solutions is
an extremely useful skill.  One of the benefits of learning math and
computer science, is that you become trained in thinking about
problems using these methods and tools.  For example, being able to
write functions, both mathematical and for computer programs, involves
precisely defining the inputs that the function works on, and the
outputs that it produces.  And, in both cases, we need to formally
define the operations that occur, so that the function always
deterministically produces the same correct results for the given
inputs.  This is one reason why thinking about and carefully
documenting your input parameters and return results for a function
are very important.
\subsection{Standard Libraries of Functions}
\label{sec-1-2}

\begin{itemize}
\item The math library
\item Need to include the header to use a standard library \#include <cmath>
\item Headers for libraries of standard functions basically define the
function signature.  We will go into more details about functions
signatures, also called function prototypes, in a bit.
\item Use some of these functions.
\item Show Fig 6.7 (pg 219), list of some of the standard libraries in C/C++.
\end{itemize}
\subsection{Defining a Function}
\label{sec-1-3}
\begin{itemize}
\item Function name (choose meaningful name)
\item Function Input (the parameters to the function)
\item Function Output (the return value)
\item Always include a function header documentation.  Document purpose,
parameters and return value.
\item Implement pow(), fabs(), maybe ceil() and floor()
\end{itemize}
\section{Second Session (11:45 - 12:30)}
\label{sec-2}

\subsection{Function prototypes}
\label{sec-2-1}
\begin{itemize}
\item The signature of a function is its prototpye.
\item To use a function, all you need is the signature.
\item This is important conceputally.  The signature represents the "black
box" idea of functions.  The details of the implementation are not
so important, at least to those who want to use the function to
solve larger problems.  They are only concerned about what it does,
how you use it, and that it performs it stated task correctly.
\item The actual implementation can be somewhere else.
\item In fact, put signatures in a header file, implementations in a separate source file, and (re)use.
\item This is the basic method used for the standard libraries of functions.
\end{itemize}
\subsection{Variable and Argument Coercion}
\label{sec-2-2}

\begin{itemize}
\item C promotes certain numeric values in mixed-type expressions.  Type
is promoted to the "highest" type in the expression.
\item \textbf{BEWARE} of the so called integer division error.
\item Passing a parameter to a function can also be automatically coerced in this way.
\end{itemize}
\section{Third Session (12:40 - 1:40)}
\label{sec-3}

\subsection{Scope Rules}
\label{sec-3-1}
\begin{itemize}
\item Variables declared in functions are local to the function.
\item Variables (and constants) declared outside of functions are global.
\item You probably should NOT be using global variables.  Global variables allow
state information to leak between functions.
\item Global constants, however, are often a good idea and useful.
\item Understanding the scope of variables is important.  Limiting scope of
variables is important.
\end{itemize}
\subsection{Passing Parameters by Reference}
\label{sec-3-2}
\begin{itemize}
\item Variables are passed to functions by value by default.
\item This means, the value is copied, and if you change value in the
function, the value is not changed in the caller.
\item The only way to get a value back to the caller, is to return it
as the return result from the function.
\item However, sometimes we need to return more than 1 value, or sometimes
for efficiency reasons (e.g. need to return 1 million values, we probably
don't really want to copy them all back).
\item In this case, we can pass in values by reference.
\item A reference parameter, if changed in the function, will be changed
for the caller who provided it.  In effect, a reference parameter is
not a copy, but it IS the actual variable from the caller, so
changes to it will be accessible to the caller when the function
returns.
\end{itemize}
\subsection{Function Call Stack}
\label{sec-3-3}
\begin{itemize}
\item Example, functions A(), B() and C()
\item Recursive
\item Some advice/examples on using the Visual Studio debugger.
\end{itemize}
% Emacs 24.3.1 (Org mode 8.2.4)
\end{document}
